Mahotas: Open source software for scriptable computer vision

### 2013-01-02 paper.tex
TXT Update performance table

So, for example, this is how \emph{erode} is implemented. \code{py\_erode}
consists mostly of boiler-plate code:

@@

\begin{table}
\centering
\begin{tabular}{lrrrrr}
\toprule
Operation & mahotas & pymorph & scikits-image & OpenCV\\
\midrule
erode       &     10.3 &     14.2 &     41.5 &      0.4 & \\
dilate      &     12.7 &      8.9 &     38.9 &      0.4 & \\
open        &     23.0 &     23.3 &     80.8 &       NA & \\
center mass &      7.1 &       NA &       NA &       NA & \\
sobel       &     75.4 &       NA &    105.4 &      6.2 & \\
cwatershed  &    191.3 &  60410.0 &    285.0 &     42.1 & \\
daubechies  &     20.3 &       NA &       NA &       NA & \\
haralick    &    304.5 &       NA &   7615.8 &       NA & \\
\bottomrule
\end{tabular}
\caption{Efficiency Results for mahotas, pymorph, scikits-image, and openCV
(through Python wrappers). Shown are values as multiples of the time that
\code{numpy.max(image)} takes to compute the maximum pixel value in the image
(all operations are over the same image). For scikits-image, features on the
grey-scale cooccurrence matrix were used instead of Haralick features, which it
does not support.}
\label{tab:efficiency}
\end{table}

@@

Among the other libraries, mahotas is the fastest. Pymorph, even though it is
implemented in Python only, intelligently uses arithmetic operations for this
operation and can be very fast. However, for more complex methods, such as
watershed; its pure Python approach is very inefficient.

@@

\textbf{Programming language}\\
Mahotas works in Python (minimal version is~2.5 and works in all more recent
versions, including in the Python~3 series).

@@

\textbf{Code repository}\\
\textit{Name}: Github\\
\textit{Identifier}: https://github.com/luispedro/mahotas\\
\textit{Licence}: MIT\\
\textit{Date published}: Since 2010. Some of the code had been previously made
available under other names.

>>>>

So, for example, this is how \emph{erode} is implemented.\footnote{This is the
generic version of the code. Erode, like a few other functions, has two
versions, a fast version, limited to two-dimensional, contiguous, images and a
generic one presented here.} \code{py\_erode} consists mostly of boiler-plate
code:

@@

\begin{table}
\centering
\begin{tabular}{lrrrrr}
\toprule
Operation & mahotas & pymorph & scikits-image & OpenCV\\
\midrule
erode                &      1.6 &     15.1 &      7.4 &      0.4 & \\
dilate               &      1.5 &      9.1 &      7.3 &      0.4 & \\
open                 &      3.2 &     24.3 &     14.8 &       NA & \\
median filter (2)    &    226.9 &       NA &   2034.0 &       NA & \\
median filter (10)   &   2810.9 &       NA &   1877.1 &       NA & \\
center mass          &      5.0 &       NA &   3611.2 &       NA & \\
sobel                &     34.1 &       NA &     62.5 &      6.2 & \\
cwatershed           &    174.8 &  58440.3 &    287.3 &     44.9 & \\
daubechies           &     18.8 &       NA &       NA &       NA & \\
haralick             &    233.1 &       NA &   7760.7 &       NA & \\
\bottomrule
\end{tabular}
\caption{Efficiency Results for mahotas, pymorph, scikits-image, and openCV
(through Python wrappers). Shown are values as multiples of the time that
\code{numpy.max(image)} takes to compute the maximum pixel value in the image
(all operations are over the same image). For scikits-image, features on the
grey-scale cooccurrence matrix were used instead of Haralick features, which it
does not support. In the case of \emph{median filter}, the radius of the
structuring element is shown in parentheses.}
\label{tab:efficiency}
\end{table}

@@

Among the other libraries, mahotas is the fastest. Pymorph, even though it is
implemented in Python only, intelligently uses arithmetic operations for this
operation and can be very fast. However, for more complex methods, such as
watershed; its pure Python approach is very inefficient. The one exception is
that median filtering with a large structuring element is faster in
scikit-image. In fact, that library uses an algorithm with better asymptotic
behavior for this operation.

@@

\textbf{Programming language}\\
Mahotas works in Python (minimal version is~2.5, but mahotas works with all
more recent versions, including version in the Python~3 series).

@@

\textbf{Code repository}\\
\textit{Name}: Github\\
\textit{Identifier}: https://github.com/luispedro/mahotas\\
\textit{Licence}: MIT\\
\textit{Date published}: Since 2010 as mahotas. Some of the code had been
previously made available under other names.
